\pkg{cubble}: An R Package for Organizing and Wrangling Multivariate Spatio-temporal Data

### 2022-06-24 3-the-cubble-pkg.Rmd
better naming of the chapters
create separate files for reproduciblity

```{r face, echo = FALSE, fig.align="center", out.width = "100%", fig.cap = "An illustration of function \\code{face\\_temporal} and \\code{face\\_spatial} in cubble. In the first row, \\code{face\\_temporal} switches a cubble from the nested form into the long form and the focus has switched from the spatial aspect (the side face) to the temporal aspect (the front face). In the second row, \\code{face\\_spatial} switches a cubble back to the nested form from the long form and shifts focus back to the spatial aspect."}
knitr::include_graphics(here::here("figures/diagram-keynotes/diagram-keynotes.002.png"))
```

@@

This function should generally be used in the last step of the analysis since it is a temporary operation, meaning that these added spatial variables will disappear if switched to the nested form and then switched back:

```{r echo = TRUE}
cubble_unfold |> face_spatial() |> face_temporal()
```

@@

```{r eval = FALSE, echo = TRUE}
# Assume my_ncdf has a bounding box of [-180, -90, 180, -90]
# at 0.25 degree resolution and subset it to have
# 1 degree resolution:
dt <- as_cubble(my_ncdf, vars = c("q", "z"),
                long_range = seq(-180, 180, 1),
                lat_range = seq(-90, 90, 1))
```

>>>>

```{r face, echo = FALSE, fig.align="center", out.height = "35%", out.width = "100%", fig.cap = "An illustration of function \\code{face\\_temporal} and \\code{face\\_spatial} in cubble. In the first row, \\code{face\\_temporal} switches a cubble from the nested form into the long form and the focus has switched from the spatial aspect (the side face) to the temporal aspect (the front face). In the second row, \\code{face\\_spatial} switches a cubble back to the nested form from the long form and shifts focus back to the spatial aspect."}
knitr::include_graphics(here::here("figures/diagram-keynotes/diagram-keynotes.002.png"))
```

@@

@@

```{r eval = FALSE, echo = TRUE}
# Assume my_ncdf has a bounding box of [-180, -90, 180, 90]
# at 0.25 degree resolution and subset it to have
# 1 degree resolution:
dt <- as_cubble(my_ncdf, vars = c("q", "z"),
                long_range = seq(-180, 180, 1),
                lat_range = seq(-90, 90, 1))
```

### 2022-06-24 4-other-features.Rmd
create separate files for reproduciblity

```{r illu-interactive, echo = FALSE, fig.align="center", out.height="40%", out.width = "100%", fig.cap = "Linking between multiple plots. The line plots and the map are constructed from shared crosstalk objects (long and nested cubbles). When a station is selected on the map (a), the corresponding row in the nested cubble will be activated. This will link to all the rows with the same id in the long cubble (b) and update the line plot (c)."}
knitr::include_graphics(here::here("figures/diagram-keynotes/diagram-keynotes.004.png"))
```

@@

An example using a glyph map is shown in Section \@ref(precip).

>>>>

```{r illu-interactive, echo = FALSE, fig.align="center", out.height = "35%", out.width = "100%", fig.cap = "Linking between multiple plots. The line plots and the map are constructed from shared crosstalk objects (long and nested cubbles). When a station is selected on the map (a), the corresponding row in the nested cubble will be activated. This will link to all the rows with the same id in the long cubble (b) and update the line plot (c)."}
knitr::include_graphics(here::here("figures/diagram-keynotes/diagram-keynotes.004.png"))
```

@@

An example using a glyph map is shown in Section \@ref(historicaltmax).

### 2022-06-24 5-2-aus-hist-max-temp.Rmd
create separate files for reproduciblity

In order to create a glyph map displaying the monthly series  (Figure \ref{fig:basic-manip}), the spatial variables need to be unfolded with the temporal variables. The reason being that the major (\code{long}, \code{lat}) and minor (\code{month}, \code{tmax}) coordinates need to be on the same table to create the glyph map. The \code{geom_glyph()} function does both the transformation and the plotting. \textcolor{green}{(An inset of the glyph for one station is shown in the top left corner.)}

@@

```{r create-inset, eval = FALSE}

tmax %>% filter(id == "ASN00048027") %>%
  ggplot(aes(x = month,
             y = tmax,
             color = group)) +
  geom_line(size = 1.5) +
  scale_color_brewer(palette = "Dark2", 
                     guide = "none") +
  scale_x_continuous(breaks = seq(1, 12, 1), 
                     labels = c("J", "F", "M", "A",
                                "M", "J", "J", "A",
                                "S", "O", "N", "D")) +
  labs(x = "", y  = "Temp (C)", 
       title = "ASN00048027: Cobar") +
  theme_bw() +
  theme(
    aspect.ratio = 0.3,
    axis.text = element_text(size = 20),
    title =  element_text(size = 20)
  )

#ggsave(filename = here::here("figures/basic-manip-inset.png"), width = 7)
```

```{r basic-manip, out.width="50%", fig.height = 6, fig.width = 5, fig.cap="A glyph map of the monthly maximum average temperature for weather stations in  Victoria and New South Wales for the periods (1971-1975, 2016-2020). The corresponding average time series for the Cobar station are display on the top left corner. From the glyph map we can observe that the monthly trend is similar for all locations (low in the winter, high in the summer), and small increased temperatures, particularly in late summer can be seen at most stations."}
tmax <- tmax %>% unfold(long, lat)

nsw_vic <- ozmaps::abs_ste %>% 
  filter(NAME %in% c("Victoria", "New South Wales"))

p1 <- ggplot() + 
  geom_sf(data = nsw_vic, fill = "grey95", 
          color = "white", size=2) + 
  geom_glyph(data = tmax, 
             aes(x_major = long, x_minor = month, 
                 y_major = lat, y_minor = tmax,
                 group = interaction(id, group), 
                 color = group),
             width = 1.2, height = 1, alpha=0.5, 
             size=1.1) +
  scale_color_brewer("", palette = "Dark2") + 
  theme_bw() + 
  coord_sf(xlim = c(141, 154), ylim = c(-39, -28.5)) + 
  ggthemes::theme_map() +
  theme(legend.position = "bottom",
        legend.text = element_text(size = 15)) #+

box_df <- tmax %>% 
  face_spatial() %>% 
  filter(id == "ASN00048027")
single <- tibble::tibble(img = here::here("figures/basic-manip-inset.png"))

p1 +
  geom_rect(data = box_df,
            aes(xmin = long - 0.6, xmax = long + 0.6,
                ymin = lat - 0.12, ymax = lat + 0.35),
            fill = "transparent", color = "black") +
  ggimg::geom_point_img(
    data = single, aes(x = 143.7, y = -30, img = img), size = 6) + 
  guides(color = guide_legend(override.aes = list(size=5)))

>>>>

In order to create a glyph map displaying the monthly series  (Figure \ref{fig:basic-manip}), the spatial variables need to be unfolded with the temporal variables. The reason being that the major (\code{long}, \code{lat}) and minor (\code{month}, \code{tmax}) coordinates need to be on the same table to create the glyph map. The \code{geom_glyph()} function does both the transformation and the plotting.

@@

```{r}
cobar <- tmax %>% filter(id == "ASN00048027") %>%
  ggplot(aes(x = month, y = tmax, color = group)) +
  geom_line() +
  scale_color_brewer(palette = "Dark2", guide = "none") +
  scale_x_continuous(
    breaks = seq(1, 12, 1), 
    labels = c("J", "F", "M", "A",
               "M", "J", "J", "A",
               "S", "O", "N", "D")
    ) +
  labs(x = "", y  = "Temp (C)") +
  theme_bw() + 
  theme(aspect.ratio = 0.3)

```{r basic-manip, fig.height=6, fig.cap="A glyph map of the monthly maximum average temperature for weather stations in  Victoria and New South Wales for the periods (1971-1975, 2016-2020). The corresponding average time series for the Cobar station are display on the top left corner. From the glyph map we can observe that the monthly trend is similar for all locations (low in the winter, high in the summer), and small increased temperatures, particularly in late summer can be seen at most stations in New South Wales."}
tmax <- tmax %>% unfold(long, lat)
box_df <- tmax %>% face_spatial() %>% filter(id == "ASN00048027")
nsw_vic <- ozmaps::abs_ste %>% filter(NAME %in% c("Victoria","New South Wales"))

p1 <- ggplot() + 
  geom_sf(data = nsw_vic, fill = "grey95", 
          color = "white", size=2) + 
  geom_glyph(
    data = tmax, 
    aes(x_major = long, x_minor = month, 
        y_major = lat, y_minor = tmax,
        group = interaction(id, group), color = group),
    width = 1.2, height = 0.8) +
    geom_rect(
      data = box_df,
      aes(xmin = long - 0.6, xmax = long + 0.6,
          ymin = lat - 0.12, ymax = lat + 0.35),
      fill = "transparent", color = "black") +
  scale_color_brewer("", palette = "Dark2") + 
  coord_sf(xlim = c(141, 154), ylim = c(-39, -28.5)) + 
  ggthemes::theme_map() +
  theme(legend.position = "bottom", legend.text = element_text(size = 15)) + 
  guides(color = guide_legend(override.aes = list(size=2)))

(cobar / p1)  + 
  patchwork::plot_layout(heights = c(1,5)) + 
  plot_annotation(tag_levels = 'a')

### 2022-06-24 5-3-river-level-rainfall.Rmd
create separate files for reproduciblity

p1 <-ggplot() + 
  geom_sf(data = vic_map, fill = "grey95", color = "white") + 
  geom_point(data = dplyr::bind_rows(river, climate), 
             aes(x = long, y = lat, color = type), alpha = 0.2, fill = 0.2) +
  geom_point(data = res, aes(x = long, y = lat, color = type)) +
  ggrepel::geom_label_repel(
    data = res %>% filter(type == "river"), aes(x = long, y = lat, label = group)) +
  scale_color_brewer(palette = "Dark2")  + 
  ggthemes::theme_map() +
  ggplot2::theme(legend.position = "bottom") +
  ggplot2::labs(x = "Longitude", y = "Latitude")

>>>>

p1 <-ggplot() + 
  geom_sf(data = vic_map, fill = "grey95", color = "white") + 
  geom_point(data = dplyr::bind_rows(river, climate), 
             aes(x = long, y = lat, color = type), alpha = 0.2, fill = 0.2) +
  geom_point(data = res, aes(x = long, y = lat, color = type)) +
  ggrepel::geom_label_repel(
    data = res %>% filter(type == "river"), aes(x = long, y = lat, label = group)) +
  scale_color_brewer(palette = "Dark2")  + 
  ggthemes::theme_map() +
  ggplot2::theme(legend.position = "bottom",
                 legend.text = element_text(size = 15),
                 legend.title = element_text(size = 15)) +
  ggplot2::labs(x = "Longitude", y = "Latitude") + 
  guides(color = guide_legend(override.aes = list(size=5)))

### 2022-06-24 5-4-era5.Rmd
create separate files for reproduciblity

```{r eval = FALSE, echo = TRUE}
raw <- ncdf4::nc_open(here::here("data/era5-pressure.nc"))
dt <- as_cubble(raw, vars = c("q", "z"))
```

@@

```{r netcdf, out.width="100%", fig.cap = "A reproduction of the second row (ERA5 data) of Figure 19 in Hersbach et al (2020) to illustrate the break-up of sourthern polar vortex in late September and early October 2002. The polar vortex, signalled by the high speicfic humidity, splits into two on 2002-09-26 and furthers split into four on 2002-10-04."}
knitr::include_graphics(here::here("figures/netcdf.png"))
```

>>>>

```{r echo = TRUE}
raw <- ncdf4::nc_open(here::here("data/era5-pressure.nc"))
dt <- as_cubble(
  raw, vars = c("q", "z"),
  long_range = seq(-180, 180, 1), lat_range = seq(-90, 90, 1))
```

@@

```{r eval = FALSE}
# prepare data/era5-pressure.nc
library(ecmwfr)
my_request <- list(
  product_type = "reanalysis",
  format = "netcdf",
  pressure_level = "10",
  year = "2002",
  month = c("09", "10"),
  day = c("04", "22", "26", "30"),
  time = "00:00",
  area = c(-5, -180, -90, 180),
  variable = c("specific_humidity", 'geopotential'),
  dataset_short_name = "reanalysis-era5-pressure-levels",
  target = "era5-pressure.nc"
)
# 
# # here you need to create an account on Climate Data Store 
# # at https://cds.climate.copernicus.eu/cdsapp#!/home) to obtain the user ID and API key
# # then set up the with ecmwfr::wf_set_key(user, key, service = "cds")
# # the user below is the same `user` in the setup line
wf_request(
  user = "113339",
  request = my_request,
  transfer = TRUE,
  path = here::here("data/"))
```

```{r netcdf,  fig.height = 4, fig.width = 10, fig.cap = "A reproduction of the second row (ERA5 data) of Figure 19 in Hersbach et al (2020) to illustrate the break-up of sourthern polar vortex in late September and early October 2002. The polar vortex, signalled by the high speicfic humidity, splits into two on 2002-09-26 and furthers split into four on 2002-10-04."}

date <- c("2002-09-22", "2002-09-26", "2002-09-30", "2002-10-04") %>% as.Date()
res <- dt %>% 
  face_temporal() %>% 
  filter(lubridate::date(time) %in% date) %>%
  unfold(long, lat) %>% 
  mutate(q =  q* 10^6)

box = c(xmin = -180, ymin = -90, xmax = 180, ymax = -5)
sf::sf_use_s2(FALSE)
country <- rnaturalearth::ne_coastline("small", returnclass = "sf") %>% 
  sf::st_crop(box) %>% 
  sf::st_cast("MULTILINESTRING")

res %>% 
  ggplot() +
  # q for specific humidity
  geom_point(aes(x = long, y = lat, color = q)) +
  # z for geopotential
  geom_contour(data = res, aes(x = long, y = lat, z = z),
               color = "grey20", binwidth = 4000, size = 0.5) +
  geom_sf(data = country , alpha = 0.5, fill = "transparent", color = "lightgreen") +
  coord_sf(
    crs = "+proj=stere +lat_0=-90 +lon_0=-180 +k=1 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs ", default_crs = sf::st_crs(4326), label_graticule = "EW") + 
  theme_bw() + 
  theme(legend.position = "bottom",
        axis.ticks = element_blank(),
        panel.border = element_blank(),
        axis.text = element_blank(), 
        panel.grid = element_blank()) + 
  facet_wrap(vars(as.Date(time)), nrow = 1, shrink = TRUE)+  
  colorspace::scale_color_continuous_sequential("Purple-Yellow", name = "Specific humidity") + 
  labs(x ="", y = "")

```

### 2022-06-24 5-5-interactive-graphics.Rmd
create separate files for reproduciblity

```{r interactive-linking, echo = FALSE, out.width="100%", out.height="23%", fig.retina = 2, dpi = 300, fig.cap = "Exploring temperature variation using linking of a map and seasonal display. Each row is a screen dump of the process. The top row shows all locations (a) and all temperature profiles (d). Selecting a particular location (Mount Elizabeth) on the map (b) produces the plot in the second row. The maximum and minimum temperatures are shown using a ribbon (e). The bottom row first selects the lowest temperature in August in the seasonal display (f), which highlights the corresponding station on the map (Thredbo AWS). Another station, located in the Tasmania Island, is then selected (c) to compare its temperature variation with Thredbo AWS.", fig.show='hold'}
knitr::include_graphics(here::here("figures/linking.png"))
knitr::include_graphics(here::here("figures/linking-north.png"))
knitr::include_graphics(here::here("figures/linking-lower.png"))
#knitr::include_graphics(here::here("figures/linking-south.png"))
```

>>>>

```{r eval = FALSE}
# This chunk generates the interactive graphic and save it as figures/linking.html, where the three screencasts in the figure comes from.
library(crosstalk)
library(plotly)

clean <- climate_full %>%
  filter(!id %in% c("ASN00067033", "ASN00072091", "ASN00059040", 
                    "ASN00097053", "ASN00040856", "ASN00015548")) %>%
  face_temporal() %>% 
  mutate(month = lubridate::month(date)) %>%
  group_by(month) %>%
  summarise(
    tmax = mean(tmax, na.rm = TRUE),
    tmin = mean(tmin, na.rm = TRUE),
    diff = mean(tmax - tmin, na.rm = TRUE)
    ) %>% 
  ungroup(month) %>%
  mutate(dummy_date = as.Date(glue::glue("2021-{month}-01"))) %>% 
  face_spatial() %>% 
  mutate(temp_diff_var = ts %>% pull(diff) %>% var(na.rm = TRUE))

nested <- clean %>% 
  SharedData$new(~id, group = "cubble")

long <- clean %>% 
  face_temporal() %>% 
  unfold(temp_diff_var) %>% 
  arrange(temp_diff_var) %>% 
  SharedData$new(~id, group = "cubble")

state_map <- rmapshaper::ms_simplify(ozmaps::abs_ste, keep = 2e-3)

p1 <- nested %>% 
  ggplot() +
  geom_sf(data = state_map, fill = "grey95", color = "white") +
  geom_point(aes(x = long, y = lat,color = temp_diff_var, label = name)) +
  colorspace::scale_color_continuous_sequential(
    "Rocket",  n_interp = 7, cmax = 90, rev = TRUE, 
    c2 = 40, l2= 85, c1 = 20, l1 = 30, name = "Var. temp. diff.") +
  labs(x = "Longitude", y = "Latitude") + 
  coord_sf() + 
  theme_bw() + 
  theme(
    panel.grid.major = element_blank(),
    legend.position = "none"
    )

p2 <- long %>% 
  ggplot(aes(x = dummy_date, group = id, 
             fill = temp_diff_var, color = temp_diff_var)) +
  geom_ribbon(aes(ymin = tmin, ymax = tmax), size = 0.1, alpha = 0.3) + 
  geom_line(aes(y = tmin), alpha = 0.1) + 
  geom_line(aes(y = tmax), alpha = 0.1) + 
  geom_point(aes(y = tmax), size = 0.1) + 
  geom_point(aes(y = tmin), size = 0.1) + 
  colorspace::scale_fill_continuous_sequential(
    "Rocket",  n_interp = 7, cmax = 90, rev = TRUE, 
    c2 = 40, l2= 85, c1 = 20, l1 = 30, name = "Var. temp. diff.") +
  colorspace::scale_colour_continuous_sequential(
    "Rocket",  n_interp = 7, cmax = 90, rev = TRUE, 
    c2 = 40, l2= 85, c1 = 20, l1 = 30, name = "Var. temp. diff.") +
  scale_x_date(date_labels = "%b", date_breaks = "1 month") + 
  labs(x = "Month", y = "Temperature") + 
  theme_bw() + 
  theme(
    panel.grid.major = element_blank(),
    legend.position = "bottom"
    )

out <- bscols(
  ggplotly(p1, width = 900, height = 700, tooltip = "label") %>%
    highlight(
      on = "plotly_selected", 
      off = "plotly_deselect", 
      opacityDim = 0.1),
  ggplotly(p2, width = 1200, height = 700, tooltip = "label") %>% 
    highlight(
      on = "plotly_selected", 
      off = "plotly_deselect", 
      opacityDim = 0.012),
  widths = c(5, 5)
)

htmltools::save_html(out, file = "figures/linking.html")

```{r interactive-linking, echo = FALSE, out.width="100%", out.height="23%", fig.retina = 2, dpi = 300, fig.cap = "Exploring temperature variation using linking of a map and seasonal display. Each row is a screen dump of the process. The top row shows all locations and all temperature profiles. Selecting a particular location on the map (here Mount Elizabeth) produces the plot in the second row. The maximum and minimum temperatures are shown using a ribbon. The bottom row first selects the lowest temperature in August in the seasonal display, which highlights the corresponding station on the map (Thredbo AWS). Another  station, located in the Tasmania Island, is then selected to compare its temperature variation with Thredbo AWS.", fig.show='hold'}
knitr::include_graphics(here::here("figures/linking.png"))
knitr::include_graphics(here::here("figures/linking-north.png"))
knitr::include_graphics(here::here("figures/linking-lower.png"))
```

### 2022-06-24 jss/cubble-jss.tex
better naming of the chapters
create separate files for reproduciblity

{\centering \includegraphics[width=1\linewidth]{../figures/diagram-keynotes/diagram-keynotes.002}

@@

This function should generally be used in the last step of the analysis since it is a temporary operation, meaning that these added spatial variables will disappear if switched to the nested form and then switched back:

\begin{CodeChunk}
\begin{CodeInput}
R> cubble_unfold |> face_spatial() |> face_temporal()
\end{CodeInput}
\begin{CodeOutput}
# cubble:  date, id [5]: long form
# bbox:    [115.97, -32.94, 133.55, -12.42]
# spatial: lat [dbl], long [dbl], elev [dbl], name [chr], wmo_id
#   [dbl]
  id          date        prcp  tmax  tmin  long   lat
  <chr>       <date>     <dbl> <dbl> <dbl> <dbl> <dbl>
1 ASN00009021 2020-01-01     0  31.9  15.3  116. -31.9
2 ASN00009021 2020-01-02     0  24.9  16.4  116. -31.9
3 ASN00009021 2020-01-03     6  23.2  13    116. -31.9
4 ASN00009021 2020-01-04     0  28.4  12.4  116. -31.9
5 ASN00009021 2020-01-05     0  35.3  11.6  116. -31.9
# ... with 1,825 more rows
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> # Assume my_ncdf has a bounding box of [-180, -90, 180, -90]
R> # at 0.25 degree resolution and subset it to have
R> # 1 degree resolution:
R> dt <- as_cubble(my_ncdf, vars = c("q", "z"),
+                 long_range = seq(-180, 180, 1),
+                 lat_range = seq(-90, 90, 1))
\end{CodeInput}
\end{CodeChunk}

@@

{\centering \includegraphics[width=1\linewidth,height=0.4\textheight]{../figures/diagram-keynotes/diagram-keynotes.004}

@@

An example using a glyph map is shown in Section \ref{precip}.

@@

{\centering \includegraphics[width=0.5\linewidth]{figures/basic-manip-1}

@@

\caption[A glyph map of the monthly maximum average temperature for weather stations in  Victoria and New South Wales for the periods (1971-1975, 2016-2020)]{A glyph map of the monthly maximum average temperature for weather stations in  Victoria and New South Wales for the periods (1971-1975, 2016-2020). The corresponding average time series for the Cobar station are display on the top left corner. From the glyph map we can observe that the monthly trend is similar for all locations (low in the winter, high in the summer), and small increased temperatures, particularly in late summer can be seen at most stations.}\label{fig:basic-manip}
\end{figure}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> raw <- ncdf4::nc_open(here::here("data/era5-pressure.nc"))
R> dt <- as_cubble(raw, vars = c("q", "z"))
\end{CodeInput}
\end{CodeChunk}

@@

{\centering \includegraphics[width=1\linewidth]{../figures/netcdf}

>>>>

{\centering \includegraphics[width=1\linewidth,height=0.35\textheight]{../figures/diagram-keynotes/diagram-keynotes.002}

@@

@@

\begin{CodeChunk}
\begin{CodeInput}
R> # Assume my_ncdf has a bounding box of [-180, -90, 180, 90]
R> # at 0.25 degree resolution and subset it to have
R> # 1 degree resolution:
R> dt <- as_cubble(my_ncdf, vars = c("q", "z"),
+                 long_range = seq(-180, 180, 1),
+                 lat_range = seq(-90, 90, 1))
\end{CodeInput}
\end{CodeChunk}

@@

{\centering \includegraphics[width=1\linewidth,height=0.35\textheight]{../figures/diagram-keynotes/diagram-keynotes.004}

@@

An example using a glyph map is shown in Section \ref{historicaltmax}.

@@

{\centering \includegraphics{figures/basic-manip-1}

@@

\caption[A glyph map of the monthly maximum average temperature for weather stations in  Victoria and New South Wales for the periods (1971-1975, 2016-2020)]{A glyph map of the monthly maximum average temperature for weather stations in  Victoria and New South Wales for the periods (1971-1975, 2016-2020). The corresponding average time series for the Cobar station are display on the top left corner. From the glyph map we can observe that the monthly trend is similar for all locations (low in the winter, high in the summer), and small increased temperatures, particularly in late summer can be seen at most stations in New South Wales.}\label{fig:basic-manip}
\end{figure}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> raw <- ncdf4::nc_open(here::here("data/era5-pressure.nc"))
R> dt <- as_cubble(
+   raw, vars = c("q", "z"),
+   long_range = seq(-180, 180, 1), lat_range = seq(-90, 90, 1))
\end{CodeInput}
\end{CodeChunk}

@@

{\centering \includegraphics{figures/netcdf-1}
